Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
chore: try to solve lukas concerns about single agent

Despite appearing centralised, this system proposes a completely decentralised execution. 
\lukas{maybe: ``While the graph, containing the aggregate information, might appear as global knowledge, this is not the case as the information is never aggregated globally. The individual nodes only combine information from their local neighbourhood.''}

@@

 It is known that \acp{GNN} have a certain ability to generalise to new structures and scale with different nodes~\cite{??}. 

@@

 During learning, it is as if we have a \emph{single} agent collectively choosing which action to take (i.e., resulting action graph). \lukas{this makes it sound like a singe agent has all information, selecting the actions for all other agents...}

>>>>

While the graph, containing the aggregate information, 
 might appear as global knowledge, 
 this is not the case as the information is never aggregated globally. 
The individual nodes only combine information from their local neighbourhood.

@@

 It is known that \acp{GNN} have a certain ability to generalise to new structures and scale with different nodes~\cite{DBLP:journals/aiopen/ZhouCHZYLWLS20,DBLP:conf/nips/KnyazevTA19}. 

@@

This is because, even though the actions are produced using only local and neighbourhood information, 
 during the learning phase, we have access to the internal graph, 
 which will influence the policy through non-local information 
 during the backpropagation.
